### 2025-08-19 chapters/benchmark.tex
new statistical findings & revised sections 4.4 & parts of 5.1

\begin{table}[htbp]
\centering
\begin{threeparttable}
\caption{Summary of workload responses to incremental hardware scaling. Negative average values indicate improved performance (lower runtime) per scaling step.}
\label{tab:hardware-impact}
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Metric} & \textbf{CPU cores} & \textbf{Memory (MB)} \\
\midrule
Workloads improved                      & 2/6 (33\%) & 2/6 (33\%) \\
Workloads slowed down                   & 2/6 (33\%) & 2/6 (33\%) \\
Workloads unaffected                    & 2/6 (33\%) & 2/6 (33\%) \\
Average performance change per step (\%)& -8.71      & -8.71      \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\footnotesize
\item Each increment corresponds to one unit increase in either CPU cores or available memory.
\item Values reflect direction and magnitude of average runtime change across all workloads.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[htbp]
\centering
\begin{threeparttable}
\caption{Summary of workload responses to incremental hardware scaling. Negative average values indicate improved performance (lower runtime) per scaling step.}
\label{tab:hardware-impact}
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Metric} & \textbf{CPU cores} & \textbf{Memory (MB)} \\
\midrule
Workloads improved                      & 2/6 (33\%) & 2/6 (33\%) \\
Workloads slowed down                   & 2/6 (33\%) & 2/6 (33\%) \\
Workloads unaffected                    & 2/6 (33\%) & 2/6 (33\%) \\
Average performance change per step (\%)& -8.71      & -8.71      \\
Median performance change per core step (\%) & -0.51      & -0.51      \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\footnotesize
\item Each increment corresponds to one unit increase in either CPU cores or available memory.
\item Values reflect direction and magnitude of average runtime change across all workloads.
\end{tablenotes}
\end{threeparttable}
\end{table}
